Visualizations for article

### 2015-12-01 101-visualizations-for-article.Rmd
Fix some bad variable names

```{r}
section_pct <- codes %>% 
  mclapply(best_section_matches, scores = scores, threshold = 0.15)  %>% 
  mclapply(summarize_borrowings) %>% 
  bind_rows()
section_pct
```

Do some filtering and munge into an edge list.

```{r}
# Note that original code is a misnomer here
edges <-
  section_pct %>% 
  mutate(original_date = extract_date(original_code),
         match_date = extract_date(match_code)) %>% 
  filter(percentage_sections >= 0.05,
         !is.na(match_code),
         original_date >= match_date) %>% 
  select(original_code, match_code, weight = percentage_sections) %>% 
  group_by(original_code) %>% 
  top_n(2, weight)
edges
```

Turn that into a graph.

```{r}
g <- graph_from_data_frame(edges, directed = TRUE) 
nodes <- distances(g, to = "NY1850", algorithm = "unweighted") %>% as.data.frame() %>% 
  add_rownames() %>% 
  rename(name = rowname, distance = NY1850) %>% 
  mutate(color = ifelse(distance == 0, "red",
                        ifelse(distance == 1, "green",
                               ifelse(distance == 2, "yellow", "lightblue"))))

nodes[nodes$name == "NY1848", "color"] <- "red"
nodes[nodes$name == "NY1849", "color"] <- "red"
nodes[nodes$name == "NY1850", "color"] <- "red"
nodes[nodes$name == "NY1851", "color"] <- "red"
g <- graph_from_data_frame(edges, directed = TRUE, vertices = nodes) 
V(g)$year <- V(g)$name %>% extract_date()
set.seed(4221)

# g <- g %>% decompose() %>% `[[`(1)

>>>>

```{r}
code_match_summary <- codes %>% 
  mclapply(best_section_matches, scores = scores, threshold = 0.15)  %>% 
  mclapply(summarize_borrowings) %>% 
  bind_rows()
code_match_summary
```

Create a network graph based on section percentages.

```{r}
edges_pct <-
  code_match_summary %>% 
  mutate(borrower_date = extract_date(borrower_code),
         match_date = extract_date(match_code)) %>% 
  filter(percentage_sections >= 0.05,
         !is.na(match_code),
         borrower_date >= match_date) %>% 
  select(borrower_code, match_code, weight = percentage_sections) %>% 
  group_by(borrower_code) %>% 
  top_n(2, weight)
edges_pct

g <- graph_from_data_frame(edges_pct, directed = TRUE) 
nodes <- distances(g, to = "NY1850", algorithm = "unweighted") %>% as.data.frame() %>% 
  add_rownames() %>% 
  rename(name = rowname, distance = NY1850) %>% 
  mutate(color = ifelse(distance == 0, "red",
                        ifelse(distance == 1, "green",
                               ifelse(distance == 2, "yellow", "lightblue"))))

nodes[nodes$name == "NY1848", "color"] <- "red"
nodes[nodes$name == "NY1849", "color"] <- "red"
nodes[nodes$name == "NY1850", "color"] <- "red"
nodes[nodes$name == "NY1851", "color"] <- "red"
g <- graph_from_data_frame(edges_pct, directed = TRUE, vertices = nodes) 
V(g)$year <- V(g)$name %>% extract_date()
set.seed(4221)
